Leveraging Diversity to Find Bugs\\ in JavaScript Engines

### 2018-08-23 paper/paper.tex
changes on intro

JavaScript (\js{}) is today one of the most popular programming
languages around~\cite{business-insider,stackify}, with penetration in
various segments including, web development, mobile, and, more
recently, the Internet of Things~(IoT)~\cite{simply-technologies}. The
interest of the community for the language encourages constant
improvements in its specification and implementations. It is natural
to expect that such improvements lead to sensible changes in engine
implementation. In fact, even small changes can have high practical impact. For
example, in October 2014 a new attribute added to Array objects
resulted in the MS Outlook Calendar web app stop working under
Chrome~\cite{array-bug-chromium-issue4247,array-bug-discussion}.

Finding bugs in \js\ engines is an important problem given the range
of applications that could be affected with those
bugs. It\Comment{Finding bugs in \js\ engines} is also
challenging. For example, a test that passes in one engine could
legitimately fail in a different engine because of some undefined
behavior in the spec\footnote{These cases of undefined behavior can be
  localized by searching for the string ``implementation-dependent''
  in the ES6 spec document~\cite{ecmas262-spec}.}. As another example,
a test may fail because the engine does not fully implement some
feature. The publicly-available Kangax compatibility
table~\cite{kangax} relates \js\ features with the engines that
support them. To sum, it is often non-trivial to assess if a test
fails because of a bug or because of some other reason making test
automation more challenging. Intuitively, developing reliable engines
is difficult because specifications are intentionally incomplete--for
development flexibility--and evolve frequently.

%% WHAT WE DID
This paper reports on a study we ran to evaluate the importance of
diversity in finding bugs on JavaScript engines. We evaluated
effectiveness of two complementary diversity-aware testing
techniques. \emph{Test transplantation} leverages diversity of test
cases to find bugs. It evaluates the effects that running \js{} test
files from a given engine have in detecting bugs in other engines. The
intuition is that developers design test cases differently; hence
replaying the test in a different engine may reveal unanticipated
problems. \emph{Cross-engine differential testing} evaluates the
ability of leveraging diversity of engine implementations to find
bugs. More precisely, it fuzzes existing test
inputs~\cite{fuzz-testing-history} and then compares the output
produced by different engines using a differential oracle. One of
various causes of output discrepancy is a bug.

>>>>

JavaScript (\js{}) is one of the most popular programming languages
today~\cite{redmonk-javascript,business-insider,stackify}, with
penetration in various segments including, web development, mobile,
and, more recently, the Internet of
Things~(IoT)~\cite{simply-technologies}. The interest of the community
for the language encourages constant improvements in its specification
and implementations. It is natural to expect that such improvements
lead to sensible changes in engine implementation. In fact, even small
changes can have high practical impact. For example, in October 2014 a
new attribute added to Array objects resulted in the MS Outlook
Calendar web app failing under
Chrome~\cite{array-bug-chromium-issue4247,array-bug-discussion}.

Finding bugs in \js\ engines is an important problem given the range
of applications that could be affected with those
bugs. It\Comment{Finding bugs in \js\ engines} is also
challenging. For example, a test that passes in one engine could
legitimately fail in a different engine because of some undefined
behavior in the spec. These cases of undefined behavior can be
localized by searching for the string ``implementation-dependent'' in
the ES6 spec document~\cite{ecmas262-spec}. As another example, a test
may fail because the engine does not fully implement some feature. The
publicly-available Kangax compatibility table~\cite{kangax} relates
\js\ features with the engines that support them. To sum, it is often
non-trivial to assess if a test fails because of a bug or because of
some other reason making test automation more challenging. Developing
reliable engines is difficult because specifications are intentionally
incomplete as to enable flexibility during development and because
they evolve frequently.

%% WHAT WE DID
This paper reports on a study we ran to evaluate the importance of
diversity in finding bugs on JavaScript engines. We evaluated
effectiveness of two complementary diversity-aware testing
techniques. \emph{Test transplantation} leverages diversity of test
cases to find bugs. It evaluates the effects that running \js{} test
files from a given engine have in detecting bugs in other engines. The
intuition is that developers design test cases with different
objectives in mind. Replaying these tests, written for a given engine,
in a different engine may reveal unanticipated
problems. \emph{Cross-engine differential testing} evaluates the
ability of leveraging diversity of engine implementations to find
bugs. More precisely, this technique fuzzes existing test
inputs~\cite{fuzz-testing-history} and then compares the output
produced by different engines using a differential oracle. The
intuition is that \Fix{...}

%One of
%various causes of output discrepancy is a bug.
